---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiDiff

This R package implements the multi-period diff-diff as discussed in Imai and Kim (2019) and Chaisemartin and Hautfeuille (2019).

## Installation


``` r
devtools::install_github("MatthieuStigler/multiDiff")
```

## Example

Main function is `DD()` (name might change!), with following arguments

- `y_var` The name of the y variable
- `treat treatment` The name of the treatment variable
- `time.index` The name of the *time* dimension variable
- `unit.index` The name of the *unit* dimension variable
- `data` The dataset

```{r}
library(multiDiff)
suppressMessages(library(tidyverse))
data <- sim_dat(N=100)
DD_out <- DD(data=data)

## Main output is:
knitr::kable(DD_out[1:5,])
```

Plot the year-by-year treatment:

```{r}
DD_out %>% 
  filter(DiD %in% c(1,4)) %>% 
  mutate(case = paste("Treat: ", treat, ", Control: ", control, sep = "")) %>% 
  ggplot(aes(x=time, y = estimate, color = case)) +
  geom_ribbon(aes(ymin = .data$conf.low, 
                    ymax = .data$conf.high,
                  group = case),
              fill = "grey", alpha = I(0.4),
              linetype = 2) +
  geom_line(size = 1) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept =1, linetype = 2) +
  ggtitle("Diff-diff by year and identification case")
```


Aggregate the results over time:

```{r}
DiD_aggreg(x=DD_out, by_DiD = FALSE)
DiD_aggreg(x=DD_out, by_DiD = TRUE)
```





