---
title: "Event_study_vs_Callaway_vs_Chaisemartin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Event_study_vs_Callaway_vs_Chaisemartin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(multiDiff)
```

Preview this file with: [link](https://htmlpreview.github.io/?https://github.com/MatthieuStigler/multiDiff/blob/master/vignettes/Event_study_vs_Callaway_vs_Chaisemartin.html)

# Comparing DiD, event-study, Callaway Sant'Anna and Chaisemartin and Haultfeuille estimates

In summary, in a *non-staggered* case:

1. a DiD estimate the average _post_ periods against all _pre_ periods
2. An event study (ES) estimates individual _post_ periods against a single _pre_ period
3. The Callaway Sant'Anna (CS) gives the same estimates as an ES when using `base_period = "universal"`
4. The CS `did::aggte` function gives the average of the _post_ periods against a single _pre_ periods
5. Therefore, the link between DiD and ES/CS is:
  - a full DiD is equal to the average ES when the ES is computed against all _pre_ periods (argument `trim_low`)
  - a truncated DiD is equal to the average ES when the DiD's input contains only one _pre_ period
5. The Chaisemartin and Haultfeuille (2023) gives the ES coefficients (against the -1 period) BUT:
  - coefficients are rounded to `digits=5`
6. The CH ATE is therefore equal to the EC/CS coefficients.


## example

Simulate data with common treatment (= non-staggered). Treatment happens at T=5.
```{r}
dat_common <- sim_dat_common(timing_treatment = 5:10, as_mdd = TRUE, seed=123)
```

Estimate the standard DiD, and a truncated DiD, where we remove all pre-treatment periods except the last one

```{r}
reg_DD <- mdd_DD_simple(dat_common)
reg_DD_trunc <- mdd_DD_simple(dat_common |>subset(Time>=4))
```

Estimate the ES coefficents

```{r}
reg_ES <- mdd_event_study(dat_common)
reg_ES_trunc <- mdd_event_study(dat_common, trim_low = -1)
```

Estimate the CS coefficients

```{r}
reg_CS <- mdd_CS(dat_common, base_period = "universal")
```

Estimate the CH coefficient

```{r}
reg_CH_24_effct_1 <- mdd_estim_CH(mdd_dat = dat_common, graph_off=TRUE)
reg_CH_24_effct_6 <- mdd_estim_CH(mdd_dat = dat_common, effects =6, placebo=3, graph_off=TRUE)
```

## verify the relationships


### The full DiD is the same as the mean ES which considers all pre-periods (`trim_low = -1`)

```{r}
all.equal(coef(reg_DD)[[1]],
          mean(coef(reg_ES_trunc)))
```

### a truncated DiD is the same as the mean ES

```{r}
all.equal(coef(reg_DD_trunc)[[1]],
          mean(coef(reg_ES)[4:9]))
```

### a truncated DiD is also the same as the `aggte(CS)`

```{r}
all.equal(coef(reg_DD_trunc)[[1]],
          suppressWarnings(did::aggte(reg_CS)$overall.att))
```

### Individual ES are equal to individual CS when using `base_period = "universal"`

```{r}
all.equal(coef(reg_ES)[4:9],
          reg_CS$att[5:10], check.attributes = FALSE)
```

### Individual ES are equal to individual CS

```{r}
all.equal(round(coef(reg_ES)[4:9],5),
          reg_CH_24_effct_6$results$Effects[,"Estimate"], check.attributes = FALSE)

```

~~~{=comment}
## render locally with: 
rmarkdown::render('vignettes/Event_study_vs_Callaway_vs_Chaisemartin.Rmd')
~~~

